How to Recognize a Bad ``Bad Smell'' using Contrast Sets

### 2016-03-10 Manuscript.tex
Updates from ShareLaTeX

\documentclass{sig-alternate}
\usepackage{tikz}
  \def\firstcircle{(90:1.75cm) circle (2.5cm)}
  \def\secondcircle{(210:1.75cm) circle (2.5cm)}
  \def\thirdcircle{(330:1.75cm) circle (2.5cm)} 
\usepackage{comment}
\usepackage{cite}
\usepackage{framed,graphicx,xcolor}

@@

\usepackage[shortlabels]{enumitem} 
\usepackage{amsmath}
\usepackage{ amssymb }
\usepackage{url}
\usepackage{balance}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\textsection\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{ 0eq:#1}}
%\setlist{nolistsep,leftmargin=5mm}
%\usepackage[pdftex]{graphicx}
\usepackage{program}
\newcommand{\Sample}{{\bf SAMPLE}}
\newcommand{\PEEKING}{{\bf PEEKING2}}
%\usepackage[table]{xcolor}
\definecolor{darkgreen}{rgb}{0,0.3,0}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{url}
\usepackage{hyperref}
%\usepackage{listings}
\DeclareMathOperator*{\argmin}{arg\,min} 
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

@@

\title{  How to Recognize  a Bad  ``Bad Smell'' using Contrast Sets}
\numberofauthors{2} 
\author{  
\alignauthor
Rahul~Krishna, Tim Menzies  \\
       \affaddr{Computer Science, NC State, USA}\\
       {\{i.m.ralk,~tim.menzies\}@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE, College Park, USA}\\ 
       {llayman@cese.fraunhofer.org}
\setlength{\columnsep}{7mm}}
\maketitle
\begin{abstract} 
It is hard to assess
if a ``bad smell'' is irrelevant or misleading
for a specific project.
Developers, text books, and tools
disagree on which bad smells are important. 
Specifically, it is unclear at what threshold values
for which metrics should trigger code reorganization\footnote{From LL: The term reorganization is a bit weird. Bad code smells are ``refactored''. Do you have a reason that you are using reorganization instead of refactoring throughout the paper? Recall that Fowler's code smell book is called ``Refactoring''} since
most studies do not offer
both metrics {\em and} a threshold for their proposed bad smells.
This paper proposes the XTREE contrast set
learner to assess bad smells
and reject any that are not supported by
evidence in the historical record.  
Using XTREE, we   show that the range of useful
``bad smells'' changes from project to project. Hence,
before refactoring, it is important to run a critique tool
like XTREE to stop work on useless code reorganizations.
Further, XTREE shows that many
of the bad smells defined in standard texts and tools
are not useful for particular projects. 
Based on these results, we endorse  
guiding code reorganization via bad smells, but one must empirically validate the importance of specific bad smells within the context of each project using an approach like XTREE.

@@

Debates on when/what code should be restructed are interesting, especially
in the current context of  widely-used SE practices such as
test-driven agile development~\cite{beck2003test,janzen05,williams2003test,george2003initial}.
In that approach, developers are always asking themselves ``should I reorganize this code''?
Bad smells are a widely used  technique for deciding when to reorganize\footnote{Fowler textbook is widely read-- as of  early 2016, ACM Digital Portal reports 
it has 6434 references. Also, bad smell-based research
is widely reported-- a search  on {\em "bad smell"+programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.}.
Hence it is important to understand the value of
 bad smells.  
Valuable development resources can be wasted if developers
change their code based on   bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

@@

%\input{tex/refactor}

@@

\subsubsection{ Shatnami}
Shatnami~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
thresholds which, following Shatnami's guidance, we set to
$p_0=p_1=0.05$. VARL encodes the defect count
for each class to 0 (for no defects known) to 1 (for defects known).
Univariate binary logistic regression is applied to learn three coefficients: $\alpha, \beta,p_0$ being
the  constant intercept ($\alpha$), the coefficient for maximizing log-likelihood function ($\beta$),
and a measure of how well this regression model predicts for the defects ($p_0$).
Any code metric with $p_0>0.05$ is then rejected as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
the equation proposed by Bender:
\begin{equation}
 \mathit{bad\; smell\; if\;} M_c > \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
\end{equation}
\subsubsection{ Alves et al.}
Alves et al.~\cite{Alves2010} propose another approach
to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
Evey metric value is weighted according to the source lines of code (LOC) of the class. All the weighted metrics are then normalized; i.e. they are divided by the sum of all weights of the same system. As with Shatnawi, univariant regression
is then applied to reject code metrics that are poor predictors of defects (i.e. all those  with $p > 0.05$).
Following this, the normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
Alves et al. then compute their 
thresholds are then derived by choosing the percentage of the overall code that needs to be represented. For instance, Alves et al. suggest the use 90\% quantile of the overall code to derive the threshold for a specific metric. The intuition here is that the worst
code are the outliers beyond 90\% of the normal code measurements.

@@

@@

Secondly, the outlier approaches described above are all 
{\em univariant} which means
they do  not understand
that sets of code metrics must
be changed at the same time.
For example:
\begin{itemize} 
\item One way to remove unusually large methods is to reorganize that method's
functionality into several smaller ones. 
\item If that is done,
this means that {\em reducing} lines of code in one method
will {\em increase} the coupling of the methods of that class to
either itself or to other classes (depending on whether or not
the new smaller methods are placed in the original class, or in other classes).
\item
Hence, it can be counter-productive to act on bad smell thresholds for {\em both}
large lines of code {\em and} seemingly excessive coupling since
one cannot be reduced without increasing the other.
\end{itemize}
\subsection{Cluster Deltas}
Borges and Menzies first proposed the centroid delta approach to avoid the drawbacks of univariant reasoning.
Centroid deltas are a {\em multivariant} method which
work  as follows:
\begin{itemize}
    \item Cluster data about code modules;
    \item Find
neighboring clusters $C_+,C_-$ where $C_+$ has more examples of defective
modules than $C_-$;
\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_+ - C_-$};
\item $\Delta$ are changes needed in defective modules of $C_+$ to
      make them more like the less-defective modules of $C_-$
\end{itemize}
Note that $\Delta$ is a multivariant recommendation
that proposes multiple changes in order to reduce defects.
Since it is computed
from neighboring clusters, it   reasons about
examples with similar distributions.  Hence,   $\Delta$  respects the naturally occurring constraints in the data. For example,
repeating the above example about large methods,   $\Delta$   will not  suggest lowering lines of code
without also increasing a coupling measure.

@@

  XTREE  is cluster delta algorithm
  that avoids the problem of verbose $\Delta$s.
  Instead of reasoning over cluster centroids,
  XTREE utilizes a decision tree learning approach
  to find the fewest differences groupings of examples.

@@

  The CART iterative dichotomization algorithm
  measures the variability of continuous attribites
  using standard deviation 
  $\sigma_x =\sqrt{ \sum^n_{i=1} \left(  \frac{(x_i - \bar{x})^2}{n-1}\right)$.
  If a code metric is split into $r$ ranges and each range is of
  size
    $n_r$ is
  associated with a set of defect counts  with standard deviation
  $\sigma_r$ then the best split is the one that minimizes
  $\sum_r\frac{n_r}{n}\sigma_x$ (where $n=\sum_r n_r$).

  \begin{figure}[t!!]
\centering
\includegraphics[width=\linewidth]{figs/XTREE_samp.png}
\caption{Sample plans from XTREE. This
tree can be read like a nested if-then-else statement. For
example, lines 3 and 8 show two branches for lines of code
(denoted here as {\em \$loc}) below 698 and above 698.
Any line with a colon ":" character  shows
a leaf of this nesting. For example, if some new code module
is passed down this tree and 
falls to the  line marked in orange,
the colon on that line indicates a 
prediction that this module has a 100\% chance of being defective.
XTREE looks for a nearby branch that has a lower chance of being
defective.
Finding the green branch, XTREE a bad smell threshold
for that module that is the delta between 
the orange branch and the green branch. In this case, that threshold
relates to 
lines of code and comments ({\em lcom}) and the cohesion between 
classes ({\em cam}:   measures similarity of
parameter list to assess the relatedness among the methods of class).
\label{fig:xtree_samp}
\end{figure}

  While not usually labelled as such, ID can
  be viewed as a clustering algorithm that groups together code modules
  with similar defect counts and some shared ranges of code metrics.
  XTREE is a post-processor to ID that reports the delta between 
  nearby groups with different defect counts. \fig{xtree_samp} offers
  a small example of that reflection. In this example:
  \begin{itemize}
      \item Some project has a table of data describing its  classes in the form of \fig{ck}.
      \item After code inspections and running test cases or operational
      tests, each such class is augmented with a defect count.
      \item CART takes that table of data and, using iterative dichotomization,
      it generated the tree of \fig{xtree_samp}.
      \item Once the tree is built, some test case arrives and is passed
      down the tree to a leaf note (see the orange line in \fig{xtree_samp}.
      \item XTREE then looks for a nearby leaf node with a lower defect
      count (see the green line in \fig{xtree_samp}. XTREE bad smell
      thresholds for that method is then the difference between 
      green and orange.
  \end{itemize}

@@

 {\em Step1:} Using the training data,  XTREE uses iterative dichotomization to
  divide a table of $N$ code modules  into  groups of
size $\alpha=\sqrt{N}$.

{\em Step2:} For each test code module, 
	  find the {\em current } leaf: take each test , run it down to a leaf in the decision tree.  
After that,	  find the {\em desired} leaf:
		\begin{itemize}[leftmargin=3mm]
		\item Starting at {\em current}, ascend the tree $lvl\in \{0,1,2...\}$ levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current }
		\item Using the {\em score} defined above, find the {\em better} siblings; i.e. those with a {\em score} less than $\gamma=0.5$ times the mean score of {\em current}. 
		   If none found, then repeat for $lvl += 1$. Also,
		    return no plan if the new $lvl$ is above the root. 
		\item  Return the {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
	 Also, find the {\em delta}; i.e. the set difference between  conditions in the decision tree branch to {\em desired} and {\em current}. To find that delta: 
	 \begin{itemize}
	     \item For discrete attributes, delta is the value from {\em desired};
	     \item For  numerics, delta is the numeric difference;
	     \item For numerics  discretized into ranges, delta is a random number selected from the low and high boundaries of the that range.
	     \end{itemize}
	     The bad smell threshold for this module is the delta that would move
	     it from the current to desired lead.

\section{Oracles}
\label{sect:eval}
\input{tex/prediction_stats.tex}

As highlighted previously, there are several detection techniques for anti-patterns, yet these fail to address the issue of checking the proposed changes for their efficacy. Much of the refactoring needs to evaluated for their usefulness. To this end, there needs to be an oracle, a procedure that can be employed to distinguish between good and bad options. The dearth oracles is not unique to this domain, for instance a recent survey by Barr et al \cite{barr15}

Our strategy (discussed in greater detail below) divides this data into a training and a testing set. The purpose of training set is twofold: (1) We apply a data miner to construct an oracle that acts as a quality predictor; (2) We build the planners to reason across the data.

Next, we employ the planners to generate plans to improve the quality of defective classes in the test set. In addition to the plans obtained from our planners we may have some common refactoring options that the developers tend to use. The oracle built previously can be used to assess the the changed examples and this can be used to compare refactoring operations.

It's worth noting that this approach depends on having effective oracles for assessing the results. It proved to be more complicated to commission the Jureczko data sets for this study. For that data, we found that the quality predictors built from this data are far from perfect; However, for some data sets, the  predictors could be salvaged using the techniques discussed in this section.

\fig{j} shows our preliminary studies with the Jureczko data. Given access to $V$ released versions, we test on version $V$ and train on the available data from $V-1$ earlier releases (as shown in \fig{j}, this means that we are training on hundreds to thousands of classes and testing on smaller test suites). Note the   \colorbox{lavenderpink}{three bottom} \colorbox{lavenderpink}{rows}   marked with $\times$: these contain predominately defective classes (two-thirds, or more).  In such data sets, it is hard to distinguish good from bad (since there are so many bad examples).

In order to identify the presence (or absence) of defects, we can consider using Boolean classes in the  Jureczko data ( \texttt{True} if defects $\gt$ 0; \texttt{False} if defects = 0). For such data, quality of the predictor can be measured using (1) the  probability of detection (a.k.a. ``pd'' or recall):  the percent of faulty classes in the test data detected by the {\em predictor}; and (2) the  probability of false alarm (a.k.a. ``pf''): the percent of non-fault classes that are {\em predicted} to be defective.

As a preliminary study, we split the Jureczko  data into train and test groups. Random Forest (again, from the SciKit learn kit~\cite{Pedregosa2012}) was built from the training data, then applied to the test data. The ``untuned'' columns of \fig{j} shows those results. We called a data set ``usable'' if Random Forest was able to classify majority of the instances correctly. For this purpose, we set a threshold of $\mathit{pd}\ge 60 \wedge \mathit{pf} \le 30$\% to select suitable data sets. With this threshold, however, none of our data sets were be suitable for this study.

@@

@@

\section{Test Data}\label{sect:tesd}

To assess our planning methods, our data (see git.io/vGYxc) comes from Jureczko et al.'s object-oriented JAVA systems~\cite{jureczko10}.

>>>>

\documentclass{sig-alternate}
\usepackage{stfloats}
\usepackage{tikz}
  \def\firstcircle{(90:1.75cm) circle (2.5cm)}
  \def\secondcircle{(210:1.75cm) circle (2.5cm)}
  \def\thirdcircle{(330:1.75cm) circle (2.5cm)} 
\usepackage{comment}
\usepackage{cite}
\usepackage{framed,graphicx,xcolor}

@@

\usepackage[shortlabels]{enumitem} 
\usepackage{amsmath}
\usepackage{ amssymb }
\usepackage{url}
\usepackage{balance}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\textsection\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
%\setlist{nolistsep,leftmargin=5mm}
%\usepackage[pdftex]{graphicx}
\usepackage{program}
\newcommand{\Sample}{{\bf SAMPLE}}
\newcommand{\PEEKING}{{\bf PEEKING2}}
%\usepackage[table]{xcolor}
\definecolor{darkgreen}{rgb}{0,0.3,0}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{url}
\usepackage{hyperref}
%\usepackage{listings}
\DeclareMathOperator*{\argmin}{arg\,min} 
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

@@

\title{  How to Recognize  a Bad  ``Bad Smell'' using Contrast Sets}
\numberofauthors{2} 
\author{  
\alignauthor
Rahul~Krishna, Tim Menzies  \\
       \affaddr{Computer Science, NC State, USA}\\
       {\{i.m.ralk,~tim.menzies\}@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE, College Park, USA}\\ 
       {llayman@cese.fraunhofer.org}
\setlength{\columnsep}{7mm}}
\maketitle
\begin{abstract} 
It is hard to assess
if a ``bad smell'' is irrelevant or misleading
for a specific project.
Developers, text books, and tools
disagree on which bad smells are important. 
Specifically, it is unclear at what threshold values
for which metrics should trigger code reorganization  since
most studies do not offer
both metrics {\em and} a threshold for their proposed bad smells.
This paper proposes the XTREE contrast set
learner to assess bad smells
and reject any that are not supported by
evidence in the historical record.  
Using XTREE, we   show that the range of useful
``bad smells'' changes from project to project. Hence,
before refactoring, it is important to run a critique tool
like XTREE to stop work on useless code reorganizations.
Further, XTREE shows that many
of the bad smells defined in standard texts and tools
are not useful for particular projects. 
Based on these results, we endorse  
guiding code reorganization via bad smells, but one must empirically validate the importance of specific bad smells within the context of each project using an approach like XTREE.

@@

Debates on when/what code should be restructed are interesting, especially
in the current context of  widely-used SE practices such as
test-driven agile development~\cite{beck2003test,janzen05,williams2003test,george2003initial}.
In that approach, developers are always asking themselves ``should I reorganize this code''?
Bad smells are a widely used  technique for deciding when to reorganize\footnote{The Fowler text is widely read-- as of  early 2016, ACM Digital Portal reports 
it has 6434 references. Also, bad smell-based research
is widely reported-- a search  on {\em "bad smell"+programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.}.
Hence it is important to understand the value of
 bad smells.  
Valuable development resources can be wasted if developers
change their code based on   bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

@@

\input{tex/refactor}

@@

\subsubsection{ Shatnami}
Shatnami~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
thresholds which, following Shatnami's guidance, we set to
$p_0=p_1=0.05$. VARL encodes the defect count
for each class to 0 (for no defects known) to 1 (for defects known).
Univariate binary logistic regression is applied to learn three coefficients: $\alpha, \beta,p_0$ being
the  constant intercept ($\alpha$), the coefficient for maximizing log-likelihood function ($\beta$),
and a measure of how well this regression model predicts for the defects ($p_0$).
Any code metric with $p_0>0.05$ is then rejected as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
the equation proposed by Bender:
\begin{equation}
 \mathit{bad\; smell\; if\;} M_c > \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
\end{equation}
\subsubsection{ Alves et al.}
Alves et al.~\cite{Alves2010} propose another approach
to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
Evey metric value is weighted according to the source lines of code (LOC) of the class. All the weighted metrics are then normalized; i.e. they are divided by the sum of all weights of the same system. For consistency
with Shatnawi, we explore the correlation between
the code metrics and the defect counts and   reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).
Following this, the normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
Alves et al. then compute their 
thresholds are then derived by choosing the percentage of the overall code that needs to be represented. For instance, Alves et al. suggest the use 90\% quantile of the overall code to derive the threshold for a specific metric. The intuition here is that the worst
code are the outliers beyond 90\% of the normal code measurements.

@@

\begin{figure*}[!b]
~\hrule~
\begin{minipage}{.53\linewidth}
\small
 \begin{tabular}{p{0.95\linewidth}} 
 On the right-hand-side is a tree
 generated by iterative dichomization. 
 This tree can be read like a nested if-then-else statement; e.g.
 \begin{itemize}
     \item Lines 3 and 8 show two branches for lines of code (denoted here as {\em `\$loc}) below 698 and above 698.
     \item Any line with a colon ":" character shows  a  leaf  of  this  nesting.   For  example,  if  some  new  code module is passed down this tree and falls to the line marked in \textcolor{orange}{{\bf orange}},  the colon on that line indicates a prediction that this module has a 100\% chance of being defective. 
     \end{itemize}
Using this tree,
 XTREE looks for a nearby branch that has a lower chance of being defective. Finding the \textcolor{green}{{\bf green}} desired  branch,  XTREE reports a bad smell threshold for that module that is the delta between the \textcolor{orange}{{\bf orange}}  current branch  and   \textcolor{green}{{\bf green}} designed branch. 
 In this case, that threshold relates to:
 \begin{itemize}
     \item Lines of code and comments ({\em lcom}) 
     \item The cohesion between classes ({\em cam}) which measures similarity of parameter lists to assess the relatedness amongst class   methods.
     \end{itemize}\\ 
 \end{tabular}
 \end{minipage}~~~~
 \begin{minipage}{.45\linewidth}
\includegraphics[width=\linewidth]{figs/XTREE_samp.png}
\end{minipage}
~\hrule~
 \caption{A brief tutorial on XTREE.} \label{fig:xtree_samp}
\end{figure*}

@@

Secondly, the outlier approaches described above are all 
{\em univariant} which means
they do  not understand
that sets of code metrics must
be changed at the same time.
For example:
\begin{itemize} 
\item One way to remove unusually large methods is to reorganize that method's
functionality into several smaller ones. 
\item If that is done,
this means that {\em reducing} lines of code in one method
will {\em increase} the coupling of the methods of that class to
either itself or to other classes (depending on whether or not
the new smaller methods are placed in the original class, or in other classes).
\item
Hence, it can be counter-productive to act on bad smell thresholds for {\em both}
large lines of code {\em and} seemingly excessive coupling since
one cannot be reduced without increasing the other.
\end{itemize}

\subsection{Cluster Deltas}

\subsubsection{CD}
Borges and Menzies first proposed the CD centroid delta approach to avoid the drawbacks of univariant reasoning~\cite{me12c}.
Centroid deltas are a {\em multivariant} method which
work  as follows:
\begin{itemize}
    \item Cluster data about code modules;
    \item Find
neighboring clusters $C_+,C_-$ where $C_+$ has more examples of defective
modules than $C_-$;
\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_+ - C_-$};
\item $\Delta$ are changes needed in defective modules of $C_+$ to
      make them more like the less-defective modules of $C_-$
\end{itemize}
Note that $\Delta$ is a multivariant recommendation
that proposes multiple changes in order to reduce defects.
Since it is computed
from neighboring clusters, it   reasons about
examples with similar distributions.  Hence,   $\Delta$  respects the naturally occurring constraints in the data. For example,
repeating the above example about large methods,   $\Delta$   will not  suggest lowering lines of code
without also increasing a coupling measure.

@@

  XTREE  is a cluster delta algorithm
  that avoids the problem of verbose $\Delta$s.
  Instead of reasoning over cluster centroids,
  XTREE utilizes a decision tree learning approach
  to find the fewest differences groupings of examples.

@@

  The CART iterative dichotomization algorithm
  measures the variability of continuous attribites
  using the  standard deviation $\sigma$ of the defect counts.
  If a code metric is split into $r$ ranges and each range is of
  size
    $n_r$ is
  associated with a set of defect counts $x$ with standard deviation
  $\sigma_r$ then the best split is the one that minimizes
  $\sum_r\frac{n_r}{n}\sigma_x$ (where $n=\sum_r n_r$).

  While not usually labelled as such, ID can
  be viewed as a clustering algorithm that groups together code modules
  with similar defect counts and some shared ranges of code metrics.
  XTREE is a post-processor to ID that reports the delta between 
  nearby groups with different defect counts. \fig{xtree_samp} offers
  a small example of that reflection. In this example:
  \begin{itemize}
      \item Some project has a table of data describing its  classes in the form of \fig{ck}.
      \item After code inspections and running test cases or operational
      tests, each such class is augmented with a defect count.
      \item CART takes that table of data and, using iterative dichotomization,
        generates the tree of \fig{xtree_samp}.
      \item Once the tree is built, some test case arrives and is passed
      down the tree to a leaf note (see the \textcolor{orange}{{\bf orange}} line in \fig{xtree_samp}.
      \item XTREE then looks for a nearby leaf node with a lower defect
      count (see the \textcolor{green}{{\bf green}} line in \fig{xtree_samp}). For that test case, XTREE proposes a bad smell
      thresholds that is  the difference between 
      \textcolor{green}{{\bf green}} and \textcolor{orange}{{\bf orange}}.
  \end{itemize}

@@

Firslty, using the training data,  XTREE uses iterative dichotomization to
  divide a table of $N$ code modules  into  groups of
size $\alpha=\sqrt{N}$.

Next, for each test code module, 
	  find the {\em current } leaf: take each test , run it down to a leaf in the decision tree.  
After that,	  find the {\em desired} leaf:
		\begin{itemize}
		\item Starting at {\em current}, ascend the tree $lvl\in \{0,1,2...\}$ levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current }
		\item Using the {\em score} defined above, find the {\em better} siblings; i.e. those with a {\em score} less than $\gamma=0.5$ times the mean score of {\em current}. 
		   If none found, then repeat for $lvl += 1$. Also,
		    return nil  if the new $lvl$ is above the root. 
		\item  Return the {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
	 Also, find the {\em delta}; i.e. the set difference between  conditions in the decision tree branch to {\em desired} and {\em current}. To find that delta,
	 for discrete attributes, delta is the value from {\em desired};
	   for  numerics, delta is the numeric difference;
	   and  for numerics  discretized into ranges, delta is a random number selected from the low and high boundaries of the that range. 
	     The bad smell threshold for   is then the delta that would move
	     the test case from the current to desired leaf.

\section{Evaluation}
\subsection{Research Questions}

Theoretically, XTREE is a good way to learn bad smell thresholds:
\begin{itemize}
    \item Unlike the outlier approach, XTREE offers bad smell
    thresholds that are specific to where test cases fall into
    the leaves of a decision tree that predicts for defects.
    That is, while the outlier approach offers one threshold for all
    metrics, XTREE specializes those thresholds to particular regions of
    the code.
    \item
    Unlike the outlier approach, XTREE is a multivariant approach
    that  understands when several code
metrics should  be changed in unison. 
\item Unlike CD, it is less verbose. 
XTREE does not report all the deltas between
adjacent clusters. Rather, it just reports the deltas in the code
metrics that a decision tree learner has determined are the minimun
changes required to distinguish one grouping from another.
\end{itemize}
Both these claims need to be tested, which leads to the following research
questions.

{\bf RQ1: Effectiveness.} {\em In a comparison of  the outlier and cluster delta
methods described above, which one reduces defects the most?}

To find an answer to this question, we will assume that developers
reorganize their code until the bad smell thresholds no longer apply.
This reorganization will start with some {\em initial} code
base that is changed to a {\em new} code base. 
For example, if the bad smell is {\em loc $>100$} and a 
code module has (e.g.) 500 lines of code, we conduct a ``what-if''
query and create a {\em new} code base with that module having {\em loc=100}.
Using a defect
predictor learned from static code metrics, we then predict the
number of defects in $d_0,d_1$ in {\em initial} and {\em new},
respectively. In this experiment,
the best bad smell threshold detector is the one that maximizes
\begin{equation}\label{eq:diff}
\mathit{improvement} = 100* \left(1 - \frac{ d_1 }{ d_0}\right)
\end{equation}

{\bf RQ2: Verbosity.}   {\em In a comparison of  the outlier and cluster delta
methods described above, which one proposes the fewest thresholds?}

Note that this is important since our goal is to critique and, possibly,
reject irrelevant bad smell detectors. As mentioned above,
  verbosity makes it hard   to critique and prune bad smells
since any bad smell mentioned by a developer has some support
somewhere amongst all those proposed thresholds.

{\bf RQ3: Co-change.}   {\em Does XTREE respect code
metrics that need to be changed together? }

For example, in XTREE's thresholds,  if {\em loc} is
reduced, does some coupling measure increase?

\input{tex/prediction_stats.tex}

\subsection{Test Data}\label{sect:tesd}

To explore these research questions,
we used data from
the Jureczko et al.'s collection of object-oriented JAVA systems~\cite{jureczko10}. To access that data, goto   git.io/vGYxc.

The Jureczko data records the number of known defects for each class using a post-release bug tracking system. The classes are described in terms of nearly two dozen metrics, included in the Chidamber and Kemerer metric suite, such as number of children (noc), lines of code (loc), etc. For details on the Jureczko code
metrics, see  \fig{ck}. For details on the rows and versions
of that data, see the left-hand-side columns of \fig{j}.

\subsection{Statistics}
Three of our methods are deterministic (Shatnami, Alves et al.,
and XTREES) while the CD uses some stochastic processing
in its clustering (CD uses the  WHERE clusterer~\cite{Menzies2013:local}). Hence, to compare all
four methods, we must run the analysis many times. 
We use  40 repeated runs, each with different random number seeds (we use 40 since that is  more than the 30 samples  needed to satisfy the central limit theorem). Each run collects the \fig{diff} values
uses defect predictions make for the {\em new} and {\em initial} code.

To rank these 40 numbers collected from CD, XTREE,Shatnami, and Alves et al.), we  use the Scott-Knott test recommended by Mittas and Angelis~\cite{mittas13}. 
In accordance to that test, using the median values of each method, we
sort a list of  $l=40$ values of \eq{diff} values found in  $ls=4$ different methods. 
Then, we split $l$ into sub-lists $m,n$ in order to maximize the expected value of differences  in the observed performances before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$: \[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]
We then apply a apply a statistical hypothesis test $H$ to check
if $m,n$ are significantly different  (in our case, the conjunction of A12 and bootstrapping). If so, Scott-Knott recurses on the splits. In other words, we divide the data if \textit{both} bootstrap sampling and effect size test agree that a division is statistically significant (with a confidence of 99\%) and not a small effect ($A12 \ge 0.6$).
For a justification of the use of non-parametric bootstrapping, see Efron \& Tibshirani~\cite[p220-223]{efron93}. For a justification of the use of effect size tests see Shepperd\&MacDonell~\cite{shepperd12a}; Kampenes~\cite{kampenes07}; and Kocaguenli et al.~\cite{Kocaguneli2013:ep}. These researchers warn that even if a hypothesis test declares two populations to be ``significantly'' different, then that result is misleading if the ``effect size'' is very small. Hence, to assess the performance differences we first must rule out small effects using A12, a test   recently endorsed by Arcuri and Briand at ICSE'11~\cite{arcuri11}.

The Scott-Knott  results are presented in the form of line diagrams like those shown on the right-hand-side of the following example table.
The black dot shows the median \eq{diff} values and the horizontal likes stretch 
from the 25th percentile to the 75th percentile (a region called the inter-quartile
range, or IQR).
\begin{center}
{\small
  Example 
\begin{tabular}{{l@{~~~}l@{~~~}r@{~~~~}r@{~~~}c@{}r}} 
\arrayrulecolor{lightgray}
\rowcolor{lightgray}\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
1 &      XTREE &    62  &  6 & \quart{47.2}{4.8}{49.6}{115}  \\
\hline 2 &      CD &    44  &  18 & \quart{28}{14.4}{35.2}{115} \\
2   & Alves        &    40  & 20  & \quart{30}{10}{50}{10}\\
\end{tabular}}
\end{center}
In this example table, the rows are  sorted on the median values of each method. Note that all the methods have \eq{diff} $\gt 0\%$; i.e. all these methods reduced the expected value of the performance score in that experiment while XTREE achieved the greatest reduction (of 62\% from the original value).
The above example table has a  left-hand-side  {\bf Rank} column, computed using the
Scott-Knott test described above. In this example table, XTREE is ranked the best, while CD and Alves  are ranked the worst.

\subsection{Orcales}
\label{sect:eval}

  An important part of this process is having an oracle
  that can assess the defect potential of the {\em initial}
  and {\em new code}. This section describes how we built
  that oracle, using Random Forests~\cite{Breiman2001}
  from the SciKit learn kit~\cite{Pedregosa2012}.
  Random Forests are a decision tree learning method but
  instead of building one tree, hundreds are built using
  randomly selected subsets of the data. The final predictions
  come from averaging the predictions over all the trees.
  Recent students rank Random Forests as  the top-most
  effective defect prediction learning algorithm~\cite{lessmann}.

\fig{j} shows our preliminary studies with Random Forests and
the Jureczko data. Given access to $V$ released versions, we test on version $V$ and train on the available data from $V-1$ earlier releases (as shown in \fig{j}, this means that we are training on hundreds to thousands of classes and testing on smaller test suites). Note the   \colorbox{lavenderpink}{three bottom} \colorbox{lavenderpink}{rows}   marked with $\times$: these contain predominately defective classes (two-thirds, or more).  In such data sets, it is hard to distinguish good from bad (since there are so many bad examples).

In order to identify the presence (or absence) of defects, we can   use Boolean classes in the  Jureczko data ( \texttt{True} if defects $\gt$ 0; \texttt{False} if defects = 0). For such data, the quality of the predictor can be measured using (1) the  probability of detection (a.k.a. ``pd'' or recall):  the percent of faulty classes in the test data detected by the {\em predictor}; and (2) the  probability of false alarm (a.k.a. ``pf''): the percent of non-fault classes that are {\em predicted} to be defective.

As a preliminary study, we split the Jureczko  data into train and test groups. Random Forests was built from the training data, then applied to the test data. The ``untuned'' columns of \fig{j} shows those results. We called a data set ``usable'' if Random Forest was able to classify majority of the instances correctly. For this purpose, we set a threshold of $\mathit{pd}\ge 60 \wedge \mathit{pf} \le 30$\% to select suitable data sets. With this threshold, however, none of our data sets were be suitable for this study.

@@

\subsection{Resylts}

It turns out that ranking code smells, and ignoring the low priority
ones, is a pressing problem. As shown in our {\em Related Work} section,
different developers and  books and tools stress the importance of different code smells. How to assess these different claims? How to avoid
needless refactoring? How to check if a code smell found at another site
is relevant to this site?

@@
